Make any stupid plot you want

### 2020-12-31 draft/sections/implementation.tex
pictures & not so many words
abstract

\begin{figure}[ht]
    \label{fig:simplex}
    \includegraphics{figures/sections/math/simplex.png}
    \caption{Simplices encode the connectivity of the data, from fully disconnected (0 simplex) observations to all observations are connected to at least 3 other observations. Higher order simplicies are outside the scope of this paper.}
\end{figure}

%% k is a triangularizable topological space 
One way to represent the topological space K is as a set composed of simplices, such as those shown in figure~\ref{fig:simplex}. Simplices are a way of encoding the connectivity of each observation ($\sigma(k)$) to another: %%formula for simplacial complexes/simplacial sets

% replace this table w/ a diagram that shows this 
\begin{description}
    \item[0-simplex] discrete observations (inventory records)
    \item[1-simplex] 1D continuos data (timeseries)
    \item[2-simplex] 2D continuos data (map)
    \item[3-simplex] 3D continuos data (video)
\end{description}
\end{document}

>>>>

\subsection{Data Model}

\end{document}

### 2020-12-31 draft/sections/math.tex
abstract

@@

\subsubsection{Visual Channels}
$\nu: \tau \mapsto \mu$ is an equivariant map such that there is a homomorphism from monoid actions on $E_{i}$ to manoid actions on $V_{i}$  
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_i \arrow[r] \arrow[r, "\nu_i"] \arrow[d, "f"'] & V_i \arrow[d, "f"] \\
    E_i \arrow[r, "\nu_i"]                           & V_i               
\end{tikzcd}
\end{equation}
where the diagram commutes such that  $\nu g(\tau_{i}) = g(\nu(tau_{i})$. Manoid actions are:
1) set of functions including identity, composition operator, closed, associative

>>>>

In our draft implementation of the data as fiber bundle model, we represent $K$ as a simplacial complex.

\begin{figure}[ht]
    \label{fig:simplex}
    \includegraphics{figures/sections/math/simplex.png}
    \caption{Simplices encode the connectivity of the data, from fully disconnected (0 simplex) observations to all observations are connected to at least 3 other observations. Higher order simplicies are outside the scope of this paper.}
\end{figure}

%% k is a triangularizable topological space 
One way to represent the topological space K is as a set composed of simplices, such as those shown in figure~\ref{fig:simplex}. Simplices are a way of encoding the connectivity of each observation ($\sigma(k)$) to another: %%formula for simplacial complexes/simplacial sets

% replace this table w/ a diagram that shows this 
\begin{description}
    \item[0-simplex] discrete observations (inventory records)
    \item[1-simplex] 1D continuos data (timeseries)
    \item[2-simplex] 2D continuos data (map)
    \item[3-simplex] 3D continuos data (video)
\end{description}

@@

\subsubsection{Visual Channels}
$\nu: \tau \mapsto \mu$ is an equivariant map such that there is a homomorphism from monoid actions on $E_{i}$ to manoid actions on $V_{i}$  
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_i \arrow[r] \arrow[r, "\nu_i"] \arrow[d, "f"'] & V_i \arrow[d, "f"] \\
    E_i \arrow[r, "\nu_i"]                           & V_i               
\end{tikzcd}
\end{equation}
where the diagram commutes such that  $\nu g(\tau_{i}) = g(\nu(tau_{i})$. Monoid actions are:
1) set of functions including identity, composition operator, closed, associative
